\TitlePt

### 2016-03-18 introduction.tex
Start review of paragraph about making an inversion

Deriving geophysical Earth models from gravity data is an inverse problem.
Designing a method for solving these inverse problems presents many challenges.
The first challenge in developing an inversion method is to establish the
functional mapping between the model parameters and the data.
This is known as the forward problem.
The forward problem must be solved in a stable and accurate way for the
inversion to succeed.
The second challenge is to choose and implement an optimization algorithm to
estimate the model parameters that best fit the observed data.
There are several well established optimization methods to choose from the
literature, for example, the gradient descent Gauss-Newton method or the
stochastic Genetic Algorithm.
The optimization algorithm is problem agnostic, meaning that it does not depend
on the type of geophysical data or parametrization used.
Finally, there is the challenge of stabilizing the inverse problem.
This is often done through some form of regulatization.
Each regularizing function favors different attributes, such as smoothness or
compactness.
Choosing an appropriate regularizing function is an indirect way to include
prior geological or geophysical information.

>>>>

Deriving geophysical Earth models from observed gravity data is an ill-posed
inverse problem.
Designing a method for solving these inverse problems presents many challenges.
The first challenge is to establish a functional mapping between the model
parameters and the data.
This is known as the forward problem and it must be solved in a stable and
accurate way for the inversion to succeed.
The second challenge is to choose and implement an optimization algorithm to
estimate the model parameters that best fit the observed data.
There are several well established optimization methods to choose from the
literature, for example, gradient-descent methods like the Gauss-Newton method
and Steepest Descent or stochastic  methods like the Genetic Algorithm.
The optimization method is independent of the forward problem.
Finally, there is the challenge of stabilizing the inverse problem.
This is often done through some form of regularization.
Each regularizing function favors different attributes, such as smoothness or
compactness.
Choosing an appropriate regularizing function is an indirect way to include
prior geological or geophysical information.
